Parsing Tweets into Universal Dependencies

### 2017-12-12 paper.tex
remove our postagger, remove normalization.

\paragraph{Acronym abbreviations.}  % How should we syntactically
% analyze acronym tokens like \emph{idc}
% (abbreviating ``I don't care'')
%  and \emph{rn} (``right now'')?  Should
% they be decomposed into their component words, and if so should those
% words be ``normalized'' into explicitly spelled out intermediate
% forms? \yicomment{this sentence should be deleted or moved to tokenization?} \yicomment{As we already know from previous sections, \emph{idc} is not tokenized and tagged as verb, we follow ...} \yicomment{Normalization is discussed in the 2.5.2 Annotation Process. Actually we did do normalization, but just as auxiliary info, didn't use it for any model.}\yjcomment{i think acronym is a different story to tokenization.}
\nascomment{removed redundant stuff here, please check}
We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate the
syntax of an acronym as a single word without normalization. Their syntactic functions
are decided according to their context. \citet{eisenstein:2013:NAACL-HLT} studied the necessity of normalization
in social media text and argued that such normalization is problematic.
Our solution to the syntax of abbreviations follows the spirit of his argument. Because abbreviations which clearly carry
syntactic functions only constitute 0.06\% of the tokens in our
dataset, we believe that normalization is an unnecessarily complicated
step.\yicomment{Again we did normalization!} \nascomment{maybe just
  add ``for acronyms'' to the end of that last sentence?}
% \nascomment{maybe we owe citations to
%   \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} here?  maybe
%   better papers to cite}

\paragraph{Non-syntactic tokens.}  
\begin{table}
\centering
\begin{tabular}{lrr}
\multicolumn{2}{r}{syntactic (\%)} & non-syntactic (\%)\\ \hline
emoticons & 0.25 & 0.95 \\
RT & 0.14 & 2.49\\
hashtag & 1.02 & 1.24 \\
URL & 0.67 & 2.38 \\
truncated words & 0.00 & 0.49 \\
 \hline
 total & 2.08 & 7.55 \\
\end{tabular}
\caption{Proportions of non-syntactic tokens in our annotation. %\yicomment{should add also retweet at-mentions}
These statistics are obtained on 140 character-limited tweets. \label{tbl:non-synt-prop}}
\end{table}

@@

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			@username \& its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http:// \& + \& RT \& pls\\
			\tiny PROPN \& \tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
		\end{deptext}
		\deproot{3}{root}
		\depedge[edge unit distance=1em]{3}{1}{vocative}
		\depedge[edge unit distance=1em]{3}{2}{nsubj}
		\depedge[edge unit distance=1em]{3}{5}{parataxis}
		\depedge[edge unit distance=1em]{5}{4}{nsubj}
		\depedge[edge unit distance=1em]{5}{6}{xcomp}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.7em]{3}{8}{parataxis}
		\depedge[edge unit distance=1em]{8}{9}{compound:prt}
		\depedge[edge unit distance=0.7em]{8}{12}{obj}
		\depedge[edge unit distance=1em]{12}{10}{nmod:poss}
		\depedge[edge unit distance=1em]{12}{11}{amod}
		\depedge[edge unit distance=0.6em]{8}{14}{obl}
		\depedge[edge unit distance=1em]{14}{13}{case}
		\depedge[edge unit distance=0.55em]{8}{16}{conj}
		\depedge[edge unit distance=1em]{16}{15}{cc}
		\depedge[edge unit distance=0.37em]{3}{17}{discourse}
	\end{dependency}
	\caption{An example tweet with informal but syntactic tokens.
		This is a contrived example inspired by several tweets.}\label{fig:informal-toks}
\end{figure*}

@@

It is important to note that these types may, in some
contexts, have syntactic functions.
For example, besides being a discourse marker, \emph{RT} can
abbreviate the verb {\tt retweet}, and emoticons and hashtags may be
used as content words within a sentence, and at-mentions can be normal vocative proper nouns; see Figure
\ref{fig:informal-toks}.  Therefore, the criteria for annotating a
token as non-syntactic must be context-dependent.
%To our knowledge, this issue has not previously been addressed in UD
%annotation efforts \nascomment{check!}\yjcomment{it's not safe to claim that.}.

@@

\subsubsection{Annotation Process}
\begin{table}
	\centering
	\begin{tabular}{rrrr}
		\hline
		& train & dev & test \\
		\hline
		tweets 		&	1,639 		&	709		&	1,201\\
		& +1,000 & +709 & +1,000\\
		tokens 		&	24,753		&	11,742	&	19,112\\
		\hline
	\end{tabular}
\caption{Statistics of {\sc Tweebank v2}.
The second row shows the number of new tweets compared to
{\sc Tweebank v1}.\label{tbl:data-stat}
}
\end{table}
Our annotation process was conducted in three stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
proportion and created the initial annotations in one day.
Before annotating, they were given a tutorial overview of the general UD
annotation conventions and our guidelines specifically for annotating tweets.
Both the guidelines and annotations
were further refined by the authors of this paper to increase
the coverage of our guidelines and solve inconsistencies between
different annotators during this exercise. In the second stage, a tokenizer, a POS tagger, and
parser were trained on the annotated data from the first stage (1,050 tweets in total),
and used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data. Finally, an extra
layer of word-level normalization\yicomment{see 10 th col of conllu
  data, also mention we could recover the original tweets also from
  this col (tokenization)}\yjcomment{didn't get your point. if
  mentioning the normalization here introduce too much confusions, we
  would better remove these.} \nascomment{I don't quite follow; maybe
  return to extra annotation done for data analysis later, when we get
to data analysis?} was manually annotated for data
analysis purposes. For example, {\em idc} is annotated as
`I\_don't\_care' and {\em 4 my FAM} is as `for my familiy'.
Such normalization doesn't change our tokenization annotation. \yicomment{should mention tokenization process, say we tokenize V1 and train tokenizer for V2 data, then manually correct them.}\yjcomment{add ``a tokenizer''}
\yicomment{add final data split}\yjcomment{it's better to use table
  \ref{tbl:data-stat}. what's more, i don't think we benefit from
  re-stating our data source.} We obtained 3,550 labelled annotated
tweets, split into train/development/test set with /(639 $+$
1000)/(210 $+$ 500)/(201 $+$ 1000) tweets, where each set consists of
both old tweets from \citet{gimpel-EtAl:2011:ACL-HLT2011} and new
tweets from the Twitter stream. \nascomment{I agree that counts and
  such should go in tables} \yicomment{should also mention main
  annotators (authors) are non-native English speakers?}
\nascomment{I'm torn about that.  has it been brought up in other datasets?}

@@

We report the inter-annotator agreement between the annotators
in the second stage. There is very little disagreement on the
tokenization annotation \nascomment{still better to quantify}.
The agreement on POS is 96.6\%, the unlabeled
dependency agreement is 88.8\% and the labeled dependency agreement
is 84.3\%. Further analysis shows the major disagreements on POS
involve entity names (30.6\%) %\yicomment{noun phrases or proper noun
                              %phrases, do we need example
                              %here?}\yjcomment{i wasn't counting
                              %PROPN and NOUN confusion, but any type
                              %of confusion related with PROPN}
                              %\nascomment{probably don't need examples}
and topical hashtags (18.1\%).
Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' 
%\yicomment{need to relate to previous error analysis, entity names
%maybe?}
can
be understood as a verbal phrase but also as the name of the Coldplay's
single and tagged as proper noun. 
%\yicomment{need to say the reason why dependency inter-annotator
%agreement is low? 1. POS disagreement lead to big difference in
%understanding the semantics. 2. Some special constructions like
%ellipsis lead to different view of tweets. Fig3 is an example of 2.}
%\nascomment{I don't think we have room to go deeper}
An example of a disagreement on
dependencies is shown in Figure \ref{fig:disagree}.  Depending on
whether this is an example of an empty auxiliary verb, or a clause-modified
noun, either annotation is plausible.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0 0 11cm 9cm},clip]{graphics/bilstm_tokenizer}
	\caption{The bi-LSTM tokenizer model that segments `its gonna be' into `it s gon na be'.}\label{fig:tok-model}
\end{figure}
We introduce a new
character-level bidirectional LSTM (bi-LSTM) sequence-labeling model
\cite{DBLP:journals/corr/HuangXY15,ma-hovy:2016:P16-1}
for tokenization.
Our model takes the raw sentence and tags each character in this 
sentence as whether it is the beginning of a word (1 as the beginning and 0 otherwise).
Figure \ref{fig:tok-model} shows our tokenization model.
Space is treated as an input but consistently assigned a special tag \$.

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & \it F1 \\
		\hline
		  Stanford CoreNLP & 96.6 \\
		 Twokenizer & 94.4 \\
% 		UD pipe v1.2 & 94.7 \\
		UD pipe v1.2 & 97.3 \\
	 	our bi-LSTM tokenizer & \bf 98.3 \\
		\hline
	\end{tabular}
	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
\end{table}

We trained our tokenizer on the training portion\yicomment{set?} of
\textsc{Tweebank v2} combined with the UD\_English training dataset
and tested on the \textsc{Tweebank v2} test set. 
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
 Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
\cite{ICWSM101540} systems are rule-based systems and were not adapted
to the UD tokenization scheme.
The UD pipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system. Compared with the UD pipe, we use LSTM
instead of GRU in our model and we also use a larger size of hidden units (64 against 20),
which has stronger representation power. 
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results indicate the value of statistical modeling
in tokenization for informal texts.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0 0 11cm 3cm},clip]{graphics/bilstm_postagger}
	\caption{The bi-LSTM POS tagger model that tags `it s gon na be' as {\tt PRON AUX VERB PART AUX}.}\label{fig:pos-model}
	%\yicomment{i'm a little confused by the pic, need discussion}
\end{figure}

Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
Twitter, we compared several existing systems and also two bi-LSTM systems similar
to \citet{DBLP:journals/corr/HuangXY15} and \citet{lample-EtAl:2016:N16-1}, one using
word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
All systems were re-trained on the combination of the UD\_English and 
\textsc{Tweebank v2} training sets. We use Twitter-specific glove embeddings released by
\citet{pennington-socher-manning:2014:EMNLP2014} in all neural taggers
and parsers.\footnote{\url{http://nlp.stanford.edu/data/glove.twitter.27B.zip}}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & \it Precision \\
		\hline
%		Stanford Postagger & 65.6 \\
		Stanford CoreNLP & 90.4 \\
%		UD pipe v1.2 & 78.7 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (greedy) & 94.2 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (CRF) & \bf 95.1 \\
		\hdashline
%		UD pipe v1.2 & 83.8 \\
		\citealp{ma-hovy:2016:P16-1} & 91.8 \\
		our word bi-LSTM & 89.2 \\
		our character + word bi-LSTMs & 91.5 \\
		\hline
	\end{tabular}
	\caption{POS tagger comparison on gold-standard tokens in the
          \textsc{Tweebank v2} test set. \label{tbl:pos-result}}
\end{table}

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & \it F1 \\
		\hline
		Stanford CoreNLP & 92.1 \\
		our bi-LSTM tokenizer (\S\ref{sec:tok}) & 93.6 \\
		\hline
	\end{tabular}
	\caption{\citet{owoputi-EtAl:2013:NAACL-HLT} POS tagging performance with automatic tokenization on
          the \textsc{Tweebank v2} test set. \label{tbl:pos-result-vs-tok}}
\end{table}

We tested the POS taggers on the \textsc{Tweebank v2} test set.  Results
with gold-standard tokenization are shown in
Table \ref{tbl:pos-result}. The careful feature engineering in the 
POS tagger of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms our neural network
models.  (That tagger also makes use of \citet{Brown:1992:CNG:176313.176316} clusters derived
from a large collection of unannotated tweets.  Those clusters did not
improve the performance of our bi-LSTM models.)

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rrcc}
		\hline
		 Pipeline stage & Score & Ours & SOTA \\
		\hline
		Tokenization  & \it $F_1$ & 98.3 & 96.6 \\		
		POS tagging &  \it Precision $F_1$ & 93.7 & 92.1 \\
		UD parsing & \it LAS $F_1$ & 74.1 & 70.3 \\
		\hline
	\end{tabular}
	\caption{Evaluating our pipeline against a state-of-the-art pipeline. \nascomment{what is ``precision $F_1$?}\label{tbl:pipline} }
\end{table}

@@

Our approach applies techniques from \newcite{DBLP:journals/corr/HintonVD15}
and \newcite{kim-rush:2016:EMNLP2016} to parsing.
Note that training a transition-based parser typically involves the
transformation of the training data into a sequence of ``oracle'' state-action
pairs.
Let $q(a \mid s)$ denote the distilled model's
probability of an action $a$ given parser state $s$; let $p(a\mid s)$ be the probability under the
ensemble (i.e., the average of the 20 separately-trained ensemble
members) \nascomment{check} \yjcomment{checked}.
To train the distilled model, we minimize the interpolation between
their distillation loss and the conventional log loss:
\begin{align}
{\argmin}_q \quad  & \alpha \sum_i \underbrace{\sum_{a} -p(a
	\mid s_i) \cdot \log q(a \mid s_i)}_{\text{distillation loss}} \\
& +\ (1 - \alpha) \sum_i \underbrace{- \log q(a_i \mid
  s_i)}_{\text{log loss}} \nonumber
\end{align}

@@

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We also compare
our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
Stanford CoreNLP tokenizer\yicomment{why not compare with UD pipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
\citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{DBLP:journals/corr/DozatM16}'s parser.
Our system differs from the SOTA pipeline in the tokenization and parser components.
From Table \ref{tbl:pipline}, our pipeline outperforms the SOTA when
evaluated in pipeline manner.
The results also emphasize the
importance of tokenization:  without gold tokenization
\nascomment{changed ``segmentation'' to ``tokenization'' here, twice}, UD parsing
performance drops by more than four points.

>>>>

\paragraph{Acronym abbreviations.}  % How should we syntactically
% analyze acronym tokens like \emph{idc}
% (abbreviating ``I don't care'')
%  and \emph{rn} (``right now'')?  Should
% they be decomposed into their component words, and if so should those
% words be ``normalized'' into explicitly spelled out intermediate
% forms? \yicomment{this sentence should be deleted or moved to tokenization?} \yicomment{As we already know from previous sections, \emph{idc} is not tokenized and tagged as verb, we follow ...} \yicomment{Normalization is discussed in the 2.5.2 Annotation Process. Actually we did do normalization, but just as auxiliary info, didn't use it for any model.}\yjcomment{i think acronym is a different story to tokenization.}
We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate the
syntax of an acronym as a single word without normalization. Their syntactic functions
are decided according to their context. \citet{eisenstein:2013:NAACL-HLT} studied the necessity of normalization
in social media text and argued that such normalization is problematic.
Our solution to the syntax of abbreviations follows the spirit of his argument. Because abbreviations which clearly carry
syntactic functions only constitute 0.06\% of the tokens in our
dataset, we believe that normalization for acronyms is an unnecessarily complicated
step.
% \nascomment{maybe we owe citations to
%   \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} here?  maybe
%   better papers to cite}

\paragraph{Non-syntactic tokens.}  
\begin{table}
\centering
\begin{tabular}{lrr}
\hline
\multicolumn{2}{r}{syntactic (\%)} & non-syntactic (\%)\\ \hline
emoticons & 0.25 & 0.95 \\
RT & 0.14 & 2.49\\
hashtag & 1.02 & 1.24 \\
URL & 0.67 & 2.38 \\
truncated words & 0.00 & 0.49 \\
 \hline
 total & 2.08 & 7.55 \\
 \hline
\end{tabular}
\caption{Proportions of non-syntactic tokens in our annotation. %\yicomment{should add also retweet at-mentions}
These statistics are obtained on 140 character-limited tweets. \label{tbl:non-synt-prop}}
\end{table}

@@

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			@username \& its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http://project\_link \& + \& RT \& pls\\
			\tiny PROPN \& \tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
		\end{deptext}
		\deproot{3}{root}
		\depedge[edge unit distance=1em]{3}{1}{vocative}
		\depedge[edge unit distance=1em]{3}{2}{nsubj}
		\depedge[edge unit distance=1em]{3}{5}{parataxis}
		\depedge[edge unit distance=1em]{5}{4}{nsubj}
		\depedge[edge unit distance=1em]{5}{6}{xcomp}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.7em]{3}{8}{parataxis}
		\depedge[edge unit distance=1em]{8}{9}{compound:prt}
		\depedge[edge unit distance=0.7em]{8}{12}{obj}
		\depedge[edge unit distance=1em]{12}{10}{nmod:poss}
		\depedge[edge unit distance=1em]{12}{11}{amod}
		\depedge[edge unit distance=0.6em]{8}{14}{obl}
		\depedge[edge unit distance=1em]{14}{13}{case}
		\depedge[edge unit distance=0.55em]{8}{16}{conj}
		\depedge[edge unit distance=1em]{16}{15}{cc}
		\depedge[edge unit distance=0.37em]{3}{17}{discourse}
	\end{dependency}
	\caption{An example tweet with informal but syntactic tokens.
		This is a contrived example inspired by several tweets.}\label{fig:informal-toks}
\end{figure*}

@@

It is important to note that these types may, in some
contexts, have syntactic functions.
For example, besides being a discourse marker, \emph{RT} can
abbreviate the verb {\it retweet}, and emoticons and hashtags may be
used as content words within a sentence, and at-mentions can be normal vocative proper nouns; see Figure
\ref{fig:informal-toks}.  Therefore, the criteria for annotating a
token as non-syntactic must be context-dependent.
%To our knowledge, this issue has not previously been addressed in UD
%annotation efforts \nascomment{check!}\yjcomment{it's not safe to claim that.}.

@@

\subsubsection{Annotation Process}
\begin{table}
	\centering
	\begin{tabular}{rrrr}
		\hline
		& train & dev & test \\
		\hline
		tweets 		&	1,639 		&	709		&	1,201\\
		& +1,000 & +709 & +1,000\\
		tokens 		&	24,753		&	11,742	&	19,112\\
		\hline
	\end{tabular}
\caption{Statistics of {\sc Tweebank v2}.
The second row shows the number of new tweets compared to
{\sc Tweebank v1}.\label{tbl:data-stat}
}
\end{table}
Our annotation process was conducted in two stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
proportion and created the initial annotations in one day.
Before annotating, they were given a tutorial overview of the general UD
annotation conventions and our guidelines specifically for annotating tweets.
Both the guidelines and annotations
were further refined by the authors of this paper to increase
the coverage of our guidelines and solve inconsistencies between
different annotators during this exercise. In the second stage, a tokenizer, a POS tagger, and
parser were trained on the annotated data from the first stage (1,050 tweets in total),
and used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data and finally achieved 3,550 labeled tweets.
Newly created annotations are splitted into train, development, and test set and appended
to the original split of {\sc Twebank v1}. Statistics of our annotations and data split are shown
in Table \ref{tbl:data-stat}.

%Finally, an extra
%layer of word-level normalization\yicomment{see 10 th col of conllu
%  data, also mention we could recover the original tweets also from
%  this col (tokenization)}\yjcomment{didn't get your point. if
%  mentioning the normalization here introduce too much confusions, we
%  would better remove these.} \nascomment{I don't quite follow; maybe
%  return to extra annotation done for data analysis later, when we get
%to data analysis?} was manually annotated for data
%analysis purposes. For example, {\em idc} is annotated as
%`I\_don't\_care' and {\em 4 my FAM} is as `for my familiy'.
%Such normalization doesn't change our tokenization annotation. \yicomment{should mention tokenization process, say we tokenize V1 and train tokenizer for V2 data, then manually correct them.}\yjcomment{add ``a tokenizer''}
%\yicomment{add final data split}\yjcomment{it's better to use table
%  \ref{tbl:data-stat}. what's more, i don't think we benefit from
%  re-stating our data source.}
%We obtained 3,550 labeled tweets, splitted them into train/development/test set.
%1000)/(210 $+$ 500)/(201 $+$ 1000) tweets, where each set consists of
%both old tweets from \citet{gimpel-EtAl:2011:ACL-HLT2011} and new
%tweets from the Twitter stream. \nascomment{I agree that counts and
%  such should go in tables} \yicomment{should also mention main
%  annotators (authors) are non-native English speakers?}
%\nascomment{I'm torn about that.  has it been brought up in other datasets?}

@@

We report the inter-annotator agreement between the annotators
in the second stage. There is very little disagreement on the
tokenization annotation. % \nascomment{still better to quantify}.
The agreement on POS is 96.6\%, the unlabeled
dependency agreement is 88.8\% and the labeled dependency agreement
is 84.3\%. Further analysis shows the major disagreements on POS
involve entity names (30.6\%) %\yicomment{noun phrases or proper noun
                              %phrases, do we need example
                              %here?}\yjcomment{i wasn't counting
                              %PROPN and NOUN confusion, but any type
                              %of confusion related with PROPN}
                              %\nascomment{probably don't need examples}
and topical hashtags (18.1\%).
Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' 
%\yicomment{need to relate to previous error analysis, entity names
%maybe?}
can
be understood as a verbal phrase but also as the name of the Coldplay's
single and tagged as proper noun. 
%\yicomment{need to say the reason why dependency inter-annotator
%agreement is low? 1. POS disagreement lead to big difference in
%understanding the semantics. 2. Some special constructions like
%ellipsis lead to different view of tweets. Fig3 is an example of 2.}
%\nascomment{I don't think we have room to go deeper}
An example of a disagreement on
dependencies is shown in Figure \ref{fig:disagree}.  Depending on
whether this is an example of an empty auxiliary verb, or a clause-modified
noun, either annotation is plausible.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0 0 11cm 9cm},clip]{graphics/bilstm_tokenizer}
	\caption{The bi-LSTM tokenizer that segments `{\it its gonna be}' into `{\it it s gon na be}'.}\label{fig:tok-model}
\end{figure}
We introduce a new
character-level bidirectional LSTM (bi-LSTM) sequence-labeling model
\cite{DBLP:journals/corr/HuangXY15,ma-hovy:2016:P16-1}
for tokenization.
Our model takes the raw sentence and tags each character in this 
sentence as whether it is the beginning of a word (1 as the beginning and 0 otherwise).
Figure \ref{fig:tok-model} shows our tokenization model.
Space is treated as an input but consistently assigned a special tag \$.

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & F1 \\
		\hline
		  Stanford CoreNLP & 96.6 \\
		 Twokenizer & 94.4 \\		 
% 		UD pipe v1.2 & 94.7 \\
		\hdashline
		UD pipe v1.2 & 97.3 \\
	 	our bi-LSTM tokenizer & 98.3 \\
		\hline
	\end{tabular}
	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
\end{table}

We trained our tokenizer on the training portion of
\textsc{Tweebank v2} combined with the UD\_English training set
and tested on the \textsc{Tweebank v2} test set. 
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
 Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
\cite{ICWSM101540} systems are rule-based systems and were not adapted
to the UD tokenization scheme.
The UD pipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system. Compared with the UD pipe, we use LSTM
instead of GRU in our model and we also use a larger size of hidden units (64 against 20),
which has stronger representation power. 
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results indicate the value of statistical modeling
in tokenization for informal texts.

@@

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=\columnwidth,trim={0 0 11cm 3cm},clip]{graphics/bilstm_postagger}
%	\caption{The bi-LSTM POS tagger model that tags `it s gon na be' as {\tt PRON AUX VERB PART AUX}.}\label{fig:pos-model}
%	%\yicomment{i'm a little confused by the pic, need discussion}
%\end{figure}

Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,derczynski-EtAl:2013:RANLP-2013,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
Twitter, we compared several existing systems which include the Stanford CoreNLP tagger, 
\citet{owoputi-EtAl:2013:NAACL-HLT}'s word cluster enhanced tagger (both in greedy and CRF), and 
also \citet{ma-hovy:2016:P16-1}'s neural network POS tagger 
which has the state-of-the-art performance  on Penn Treebank data.
 %and also two bi-LSTM systems similar
%to \citet{DBLP:journals/corr/HuangXY15} and \citet{lample-EtAl:2016:N16-1}, one using
%word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
All systems were re-trained on the combination of the UD\_English and 
\textsc{Tweebank v2} training sets. We use Twitter-specific glove embeddings released by
\citet{pennington-socher-manning:2014:EMNLP2014} in all neural taggers
and parsers.\footnote{\url{http://nlp.stanford.edu/data/glove.twitter.27B.zip}}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & Precision \\
		\hline
%		Stanford Postagger & 65.6 \\
		Stanford CoreNLP & 90.4 \\
%		UD pipe v1.2 & 78.7 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (greedy) & 94.2 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (CRF) & 95.1 \\
		\hdashline
%		UD pipe v1.2 & 83.8 \\
		\citealp{ma-hovy:2016:P16-1} & 91.8 \\
%		our word bi-LSTM & 89.2 \\
%		our character + word bi-LSTMs & 91.5 \\
		\hline
	\end{tabular}
	\caption{POS tagger comparison on gold-standard tokens in the
          \textsc{Tweebank v2} test set. \label{tbl:pos-result}}
\end{table}

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & F1 \\
		\hline
		Stanford CoreNLP & 92.1 \\
		our bi-LSTM tokenizer (\S\ref{sec:tok}) & 93.6 \\
		\hline
	\end{tabular}
	\caption{\citet{owoputi-EtAl:2013:NAACL-HLT} POS tagging performance with automatic tokenization on
          the \textsc{Tweebank v2} test set. \label{tbl:pos-result-vs-tok}}
\end{table}

We tested the POS taggers on the \textsc{Tweebank v2} test set.  Results
with gold-standard tokenization are shown in
Table \ref{tbl:pos-result}. The careful feature engineering and making use of
\citet{Brown:1992:CNG:176313.176316} clusters in the 
POS tagger of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms \citet{ma-hovy:2016:P16-1}'s neural network
model. 
%tagger
%also makes use of clusters derived
%from a large collection of unannotated tweets. % Those clusters did not
%improve the performance of our bi-LSTM models.)

@@

@@

Our approach applies techniques from \newcite{DBLP:journals/corr/HintonVD15}
and \newcite{kim-rush:2016:EMNLP2016} to parsing.
Note that training a transition-based parser typically involves the
transformation of the training data into a sequence of ``oracle'' state-action
pairs.
Let $q(a \mid s)$ denote the distilled model's
probability of an action $a$ given parser state $s$; let $p(a\mid s)$ be the probability under the
ensemble (i.e., the average of the 20 separately-trained ensemble
members).
To train the distilled model, we minimize the interpolation between
their distillation loss and the conventional log loss:
\begin{align}
{\argmin}_q \quad  & \alpha \sum_i \underbrace{\sum_{a} -p(a
	\mid s_i) \cdot \log q(a \mid s_i)}_{\text{distillation loss}} \\
& +\ (1 - \alpha) \sum_i \underbrace{- \log q(a_i \mid
  s_i)}_{\text{log loss}} \nonumber
\end{align}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rrcc}
		\hline
		\it Pipeline stage & Score & Ours & SOTA \\
		\hline
		Tokenization  & \it $F_1$ & 98.3 & 96.6 \\		
		POS tagging &  \it  $F_1$ & 93.7 & 92.1 \\
		UD parsing & \it LAS $F_1$ & 74.1 & 70.3 \\
		\hline
	\end{tabular}
	\caption{Evaluating our pipeline against a state-of-the-art pipeline. \label{tbl:pipline} }
\end{table}

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We also compare
our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
Stanford CoreNLP tokenizer, %\yicomment{why not compare with UD pipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
\citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{DBLP:journals/corr/DozatM16}'s parser.
Our system differs from the SOTA pipeline in the tokenization and parser components.
From Table \ref{tbl:pipline}, our pipeline outperforms the SOTA when
evaluated in pipeline manner.
The results also emphasize the
importance of tokenization:  without gold tokenization
%\nascomment{changed ``segmentation'' to ``tokenization'' here, twice},
UD parsing
performance drops by more than four points.
